---
title: "Untitled"
author: "Tom Klotz"
date: "30 7 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Überarbeitung für den DACH Raum

```{r}
popdictR::gruendl_terms

dfClara$pattern
```


#0.4375000
"auf kosten de(s|r) österreich(er|ers|erinnen|erin|ischer|ischen)"
"auf kosten de(s|r) deutsche(n|r)" 
"auf kosten de(s|r) schweizer(s|innen|in|ischer|ischen)?"                                                                                             

#0.8000000
"österreichische(n|r)? tradition(en)?"
"deutsche(n|r)? tradition(en)?"
"schweizer tradition(en)?"                                                                                                                            

#0.0000000
"(a|ä)ngst(e)? (de(s|r)|eine(s|r)|unsere(s|r)) österreich(er|ers|erinnen|erin|ischer|ischen)"
"(a|ä)ngst(e)? (de(s|r)|eine(s|r)|unsere(s|r)) schweizer(s|innen|in|ischer|ischen)?"
"(a|ä)ngst(e)? (de(s|r)|eine(s|r)|unsere(s|r)) deutsche(n|r)" 


##1.0000000 
"durchschnittlich(e|er|es|en|em) österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)" 
"durchschnittlich(e|er|es|en|em) deutsche(n|r|s|m)?"
"durchschnittlich(e|er|es|en|em) schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?"

#0.3928571
"zu( )?lasten de(s|r) deutsche(n|r)"                                                                                                                  
"zu( )?lasten de(s|r) österreich(er|ers|erinnen|erin|ischer|ischen)"
"zu( )?lasten de(s|r) schweizer(s|innen|in|ischer|ischen)?"  

#1.0000000                                                       
"durchschnitts(-)?schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?"
"durchschnitts(-)?österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)"
"durchschnitts(-)?deutsche(n|r|s|m)?"                                                                                                                 

#0.2857143
"(.*)arbeitend(e|er|es|en|em) deutsche(n|r|s|m)?"                                                                                                     
"(.*)arbeitend(e|er|es|en|em) österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)"                                                  
"(.*)arbeitend(e|er|es|en|em) schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?"



```{r}
dfDACH <- data.frame(list(
  pattern = c("auf kosten de(s|r) österreich(er|ers|erinnen|erin|ischer|ischen)","auf kosten de(s|r) schweizer(s|innen|in|ischer|ischen)?","österreichische(n|r)? tradition(en)?", "schweizer tradition(en)?", "(a|ä)ngst(e)? (de(s|r)|eine(s|r)|unsere(s|r)) österreich(er|ers|erinnen|erin|ischer|ischen)","(a|ä)ngst(e)? (de(s|r)|eine(s|r)|unsere(s|r)) schweizer(s|innen|in|ischer|ischen)?","durchschnittlich(e|er|es|en|em) schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?","durchschnittlich(e|er|es|en|em) österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)", "zu( )?lasten de(s|r) österreich(er|ers|erinnen|erin|ischer|ischen)", "zu( )?lasten de(s|r) schweizer(s|innen|in|ischer|ischen)?", "durchschnitts(-)?schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?", "durchschnitts(-)?österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)", "(.*)arbeitend(e|er|es|en|em) österreich(er|ers|ern|erinnen|erin|ische|ischer|isches|ischen|ischem)", "(.*)arbeitend(e|er|es|en|em) schweizer(s|n|innen|in|ische|ischer|isches|ischen|ischem)?" ),
  weight = c(0.4375000, 0.4375000, 0.8, 0.8, 0, 0, 1, 1, 0.3928571, 0.3928571, 1, 1, 0.2857143, 0.2857143 ))
)

dfDACH$pattern <- make_patterns_compound(dfDACH$pattern)

dfClaraDACH <- rbind(dfClara, dfDACH)

saveRDS(dfClaraDACH, file = "dfClaraDACH.RDS")

```

